Demes: a specification for interchanging complex demography

### 2022-04-19 paper.tex
small fixup

Demes is designed to interface with a large number of simulation and inference
methods, so we have restricted to the specification to only describe
demographic features at the population level. As the underlying discrete
demographic structure is the common thread connecting many widely used
population genetic methods, many features of underlying genome biology are
omitted. Most notably, mutation and recombination rates are left unspecified
(though they can be encoded as metadata in the data structure), as are
sequence length or annotations or genomic features.
Genome ploidy is left ambiguous, and selection and dominance models are absent. 
We also omit information about the sampling of individuals, as we view
the demographic history as independent of the sampling of individuals.
It is therefore left up to simulation and inference tools how to define
genomic parameters and sampling strategies, as each software will have its
own set of constraints and relevant input parameters.

>>>>

Demes is designed to interface with a large number of simulation and inference
methods, so we have restricted to the specification to only describe
demographic features at the population level. As the underlying discrete
demographic structure is the common thread connecting many widely used
population genetic methods, many features of underlying genome biology are
omitted. Most notably, mutation and recombination rates are left unspecified
(though they can be encoded as metadata in the data structure), as are
sequence length, annotations and other genomic features, and individual ploidy.
Selection and dominance models are absent, as discussed in
Sec.~\ref{sec:appendix-pop-gen-model}.
We also omit information about the sampling of individuals, as we view
the demographic history as independent of the sampling of individuals.
It is therefore left up to simulation and inference tools how to define
genomic parameters and sampling strategies, as each software will have its
own set of constraints and relevant input parameters.
